Rotations and Insecticide Resistance initial plots

### 2017-10-05 inst/documents/rotations_notes.Rmd
fixed setting exposures differently for each insecticide

>>>>

I now have run_rot() working for flexible numbers of insecticides (1-5).

done : Next, get active and refuge onto the same plots.  
done : allowed starting frequencies to be set

implemented set_expsoure_rot() but currently changing exposure seems to make no difference ?
dfr <- run_rot(rotation_interval=50, expo_hi=0.9)
dfr <- run_rot(rotation_interval=50, expo_hi=0.2)
# these produce identical frequency curves for r1 & r2
dfr <- run_rot(n=2, rotation_interval=50, expo_hi=c(1,0.1))

# TODO
~ implement set_exposure_rot() to replace test version

~ test setting inputs correctly (move away from hardcoded test functions)
~ find what went wrong when I set fitnesses
~ get Ian to pull changes

# state of play
~ rotations1.Rmd : example plots
